{\LARGE \textsc{Structural controlability of pollination networks}}

### 2016-05-06 paper/manuscript.Rnw
update agradecimientos

The authors thank Dr. Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Bernat Bramon, Matthew Hutchinson and Marilia Gaiarsa for feedback in early stages of the project. EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a travel grant from the European Space Agency and a Rutherford Discovery Fellowship (to DBS). DBS ackloledges the support of a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.

>>>>

The authors thank Dr. Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Bernat Bramon, Matthew Hutchinson and Marilia Gaiarsa for feedback in early stages of the project. EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency. DBS ackloledges the support of a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.
